---
title: "Simple logistic regression in R"
output: html_notebook
---

The data was dowloaded from Kaggle https://www.kaggle.com/andrewmvd/heart-failure-clinical-data


```{r}
setwd("C:/Users/golovach/Desktop/Projects/4_Heart Failure Prediction")
heart_failure_data<-read.table('heart_failure_clinical_records_dataset.csv', header=TRUE, sep = ',')
head(heart_failure_data)
```

exporing the data
```{r}
summary(heart_failure_data)
```
splitting the data into train (75%) and test (25%) sets 
```{r}
smp_size <- floor(0.75 * nrow(heart_failure_data))
```
set the seed to make  partition reproducible
```{r}
set.seed(123)
train_ind <- sample(seq_len(nrow(heart_failure_data)), size = smp_size)
train <- heart_failure_data[train_ind, ]
test <- heart_failure_data[-train_ind, ]
test_args<- subset(test, select = -DEATH_EVENT )
head(test)
head(test_args)
```
modeling the logistic regression
```{r}
mylogit_all <- glm(DEATH_EVENT ~ ., data=train, family = "binomial"(link="logit"))
summary(mylogit_all)
```

removing arguments with not significant p value (we would assume that p<0.05 is significant)
```{r}
mylogit_cut <- glm(DEATH_EVENT ~ age+ejection_fraction+serum_creatinine+time, data=train, family = "binomial"(link="logit"))
summary(mylogit_cut)
```
Confident intervals
```{r}
confint(mylogit_cut)
```
predicting the data on test data set
```{r}
fit<-predict(mylogit_cut,test_args, type = "response")
```
calculation the cutoff (number between 0 and 1)
```{r}
library(InformationValue)
optCutOff <- optimalCutoff(test$DEATH_EVENT, fit)[1] 
optCutOff

```
missclassification error
```{r}
misClassError(test$DEATH_EVENT, fit, threshold = optCutOff)

```
sensitivity
```{r}
sensitivity(test$DEATH_EVENT, fit, threshold = optCutOff)

```
specificity
```{r}
specificity(test$DEATH_EVENT, fit, threshold = optCutOff)

```
confusion matrix
```{r}
confusionMatrix(test$DEATH_EVENT, fit, threshold = optCutOff)
```

